### 2013-02-13 exam5/1.tex
extra credit

\textbf{Extra Credit}
\\
\noindent
After Van Horn discovered the problems with numbers, he attempted to
fix them.  Unfortunately, not only did he not fix them, he broke
booleans as well.  Fortunately, we have an idea about how you can
help, expressed in the following interface definitions.

\begin{verbatim}
;; A Bool implements:
;; - branch : [Action X] [Action X] -> X
;;   run the first action if this bool is true, 
;;   otherwise run the second action

;; An [Action X] implements:
;; - run : -> X
;; run this action

\end{verbatim}

Following these interface definitions, design data and class
defintions for implementations of the \verb|Bool| interface, and
reimplement the \verb|fact| method to use them.
You will need to provide new defintions for \verb|true| and
\verb|false|, since they were broken by this catastrophe as well.

@@

\begin{solution}
\begin{alltt}
\rubricpts{5 pts -- get it right}
(define-class fact%
  (define (fact n)
    (n . zero? . branch (new const% one) (new recur% n))))

(define-class const%
  (fields run))

(define-class recur%
  (fields n)
  (define (run) 
    ((new fact%) . fact (this . n . sub1) . times (this . n))))

(define-class t%
  (define (branch t e) (t . run)))
(define-class f%
  (define (branch t e) (e . run)))

(define true (new t%)) 
(define false (new f%))

(check-expect ((new fact%) . fact zero) one)                  ; 0! = 1
(check-expect ((new fact%) . fact one) one)                   ; 1! = 1
(check-expect ((new fact%) . fact (one . add1)) (one . add1)) ; 2! = 2
(check-expect ((new fact%) . fact (one . add1 . add1))        ; 3! = 6
              (one . add1 . add1 . add1 . add1 . add1))
\end{alltt}
\end{solution}
\end{problem}
\end{document}

>>>>

\textbf{Extra Credit}
\\
\noindent
Labich was unhappy to discover that the class languages don't have his
favorite programming language feature---pattern matching.  After
thinking hard about this problem, he came up with a solution, which he
calls \emph{pattern objects}.

Consider the following data defintion:
\begin{verbatim}
;; A BTree is one of:
;; - (new leaf% Number)
;; - (new node% BTree Number BTree)
;; and implements
;; - match : [Pattern X] -> X
;;   applies the given pattern object to this tree

;; A [Pattern X] implements:
;; - leaf : Number -> X
;; - node : BTree Number BTree -> X

(define-class leaf%
  (fields n)
  ;; apply the appropriate method from the given pattern object
  (define (match p) (p . leaf (this . n))))

(define-class node%
  (fields left n right)
  ;; apply the appropriate method from the given pattern object
  (define (match p) 
    (p . node (this . left) (this . n) (this . right))))
\end{verbatim}

A pattern object is like the implementation of two different functions
at once: one that implements a function for leaves from a binary tree,
and one function that works on nodes.

Write a pattern object that computes the product of all of the numbers
in a binary tree.

@@

\begin{solution}
\begin{alltt}
\rubricpts{5 pts -- get it right}
;; product% implements [Pattern Number]
(define-class product%
  ;; the product of a leaf
  (define (leaf n) n)
  ;; the product of a node
  (define (node l n r) (* n (l . match this) (r . match this))))

(define p (new product%))
(check-expect ((new leaf% 5) . match p) 5)
(check-expect ((new node%  (new leaf% 2) 5 (new leaf% 7)) . match p) 70)
\end{alltt}
\end{solution}
\end{problem}
\end{document}
